\chapter{Continuity in multiple dimensions}

\begin{definition}[Convergence in $R^n$]
	Let $(x_k)_{k \in \N}$ with $x_k = (x_{k,q},...,x_{k_n}) \in \R^n$ and $y \ in \R^n$. 
	The sequence $x_k \to^{k\to\infty} y$ iff one of the following holds:
	\begin{enumerate}
		\item For each i, the sequence $(x_{x,i})$ of real numbers converges to $y_i$.
		\item The sequence of real numbers $||x_k - y||$ converges to 0.
	\end{enumerate}
\end{definition}

\begin{definition}[Continuity]
	Let $f: \Omega \subset \R^n \to \R^m$.
	$f$ is continuous iff $\forall x_0 \in \Omega: \ \lim_{x \to x_0} f(x) = F(x_0)$.
\end{definition}

\begin{theorem}
	If $lim_{k \to \infty}a_k = a$ and  $lim_{k \to \infty} b_k = b$, $lim_{k \to \infty}a_k+b_k = a=b$ and  $lim_{k \to \infty}a_kb_k = ab$ 
\end{theorem}

\begin{proposition}[Continuity of composition]
	If $f: X \to Y$ and $g: Y \to \R^m$ are continuous, then so is their composite $g \circ f$.
\end{proposition}

\begin{remark}
    Im 2-dimensionalen Fall kann man die Stetigkeit einer Funktion mit dem "Polarkoordinaten-Trick" zeigen: Man ersetzt $x = r\cos{\phi}$ und $y = r\sin{\phi}$ und bildet den Grenzwert $\lim_{r \to 0}$. Falls das Resultat von $\phi$ abhängt, exisitiert der Grenzwert nicht. Beachte $r$ ist immer positiv somit gilt $\sqrt{r^2} = r$ (ohne Betragsstriche).
\end{remark}

\begin{definition}[Bounded, closed, compact, open sets]
	\begin{enumerate}
		\item $X \subset \R^n$ is \textbf{bounded} if the set $\{||x|| \ | \ x \in X\}$ is bounded in $R$.
		\item $X \subset \R^n$ is \textbf{closed} if for every sequence $(x_k) \in X$ converging to $y \in \R^n$, $y \in X$.
		\item $X \subset \R^n$ is \textbf{compact} if it is bounded and closed.
		\item $X \subset \R^n$ is \textbf{open} if $\forall x \in X$ there exists a $\delta > 0$ st:
			$$\{y \in \R^n | \forall i: |x_i -y_i| < \delta\}$$
			is contained in $X$.
	\end{enumerate}
\end{definition}

\begin{proposition}
	Let $f: \R^n \to \R^m$ be continuous.
	For any closed set $Y \subset \R^m$, $$f^{-1} = {x\in \R^n | f(x) \in Y} \subset \R^n$$ is closed.
\end{proposition}

\begin{theorem}[Min \& Max on compact sets]
	If $f: X \subset \R^n$ continuous, with $X$ non-empty compact set, then $f$ is bounded and achieves its max and min.
\end{theorem}

\begin{proposition}
	The set $X \subset \R^n$ is \textbf{open} iff its compement is closed.
\end{proposition}

\begin{corollary}
	For $F: \R^n \to \R^m$ continuous and $Y \subset \R^m$ open, $f^{-1}(Y)$ is open.
\end{corollary}

\begin{remark}
    \textcolor{red}{insert Grenwerte}
\end{remark}
